Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-28 ms.tex
table formatting - aleksey, please take note

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccc}
  \hline
  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$}  \\
  \hline
 & & & $\Gamma^{(a)} = 0.8$ & & & & & \\
\hline
  $    10^{ 6 }$ & 300 & 100 & $ 1.3 \times 10^{ -5 }$ & $ 1.1 \times 10^{ 2 }$ \\
  $    10^{ 6 }$ & 600  & 100 & $ 2.2 \times 10^{ -6 }$ & $ 8.1 \times 10^{ 3 }$ \\
  $    10^{ 6 }$ & 1200  & 100 & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ \\
  $    10^{ 7 }$ & 300 & 100 & $ 1.0 \times 10^{ -4 }$ & 6.5 \\
  $    10^{ 7 }$ & 600  & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ \\
  $    10^{ 7 }$ & 1200  & 100 & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ \\
  $    10^{ 8 }$ & 300 & 100 & $ 6.6 \times 10^{ -4 }$ & $\mathbf{1.4}$ \\
  $    10^{ 8 }$ & 600  & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ \\
  $    10^{ 8 }$ & 1200  & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ \\
  $    10^{ 7 }$ & 300  & 25 & $ 7.8 \times 10^{ -5 }$ & 17 \\
  $    10^{ 7 }$ & 300  & 50 & $ 7.9 \times 10^{ -5 }$ & 12 \\
  $    10^{ 7 }$ & 300  & 200 & $ 1.2 \times 10^{ -4 }$ & $\mathbf{4.7}$ \\
  $    10^{ 7 }$ & 300  & 400 & $ 3.6 \times 10^{ -4 }$ & $\mathbf{1.2}$ \\
  $    10^{ 8 }$ & 300  & 25 & $ 1.9 \times 10^{ -4 }$ & 12 \\
  $    10^{ 8 }$ & 300  & 50 & $ 3.3 \times 10^{ -4 }$ &
  $\mathbf{4.6}$ \\
  $    10^{ 8 \dagger}$ & 300  & 50 & $ 9.1 \times 10^{ -4 }$ &
  $\mathbf{5.6}$ \\
  $    10^{ 8 }$ & 300 & 200 & $ 1.4 \times 10^{ -3 }$ &
  $\mathbf{0.43}$ \\
  \hline
 & & & $\Gamma = 0.1$ & & & & & & \\
  \hline
  $    10^{ 6 }$ & 1200  & 100 & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ \\
  $    10^{ 7 }$ & 1200  & 100 & $ 5.1 \times 10^{ -7 }$ & $ 9.4 \times 10^{ 4 }$ \\
  $    10^{ 8 }$ & 1200 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2.1 \times 10^{ 4 }$ \\
  $    10^{ 8 }$ & 1200  & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3.1 \times 10^{ 4 }$ \\
  $    10^{ 8 }$ & 1200  & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ \\
  $    10^{ 8 }$ & 1200  & 400 & $ 1.2 \times 10^{ -3 }$ & $\mathbf{4.6}$ \\
  $    10^{ 8 }$ & 600  & 100 & $ 8.0 \times 10^{ -4 }$ & $\mathbf{1.6}$ \\
  $    10^{ 6 }$ & 600  & 25 & $ 1.6 \times 10^{ -6 }$ & $ 1.6 \times 10^{ 3 }$ \\
  $    10^{ 6 }$ & 600  & 50 & $ 1.7 \times 10^{ -5 }$ & $\mathbf{33}$ \\
  $    10^{ 7 }$ & 600  & 25 & $ 8.5 \times 10^{ -6 }$ & $ 4.6 \times 10^{ 2 }$ \\
  $    10^{ 7 }$ & 600  & 50 & $ 4.5 \times 10^{ -5 }$ & $\mathbf{21}$ \\
  $    10^{ 8 }$ & 600  & 25 & $ 2.3 \times 10^{ -5 }$ & $ 2.8 \times 10^{ 2 }$ \\
  $    10^{ 8 }$ & 600  & 50 & $ 6.0 \times 10^{ -5 }$ & 56 \\
  $    10^{ 8 }$ & 300  & 50 & $ 6.0 \times 10^{ -5 }$ & 56 \\
  \hline
\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
Eddington units, normalized to a stellar mass input parameter $\eta =
0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
stagnation radius.  Thermally unstable solutions are shown in bold
text.
 {\bf  BDM: (3) make sure all combinations of vw and mbh
  are included. AG: Realized that the solution I ran earlier, with
  cooling was actually a solution that would be thermally unstable
  according to our thermal instability. I am worried that this
  solution may not be representative due to the small break radius.}
\end{tablenotes}
\end{minipage}
\end{threeparttable}

>>>>

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccc}
  \hline
  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$}  \\
 & ($M_{\odot}$) & (km s$^{-1}$) & (pc) & & & & & \\ 
\hline
 & & & $\Gamma^{(a)} = 0.8$ & & & & & \\
  $    10^{ 6 }$ & 300 & 100 & & $ 1.3 \times 10^{ -5 }$ & $ 1.1 \times 10^{ 2 }$ \\
  ... & 600  & 100 & &$ 2.2 \times 10^{ -6 }$ & $ 8.1 \times 10^{ 3 }$ \\
   ...    & 1200  & 100 & &$ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ \\
  $    10^{ 7 }$ & 300 & 100 & & $ 1.0 \times 10^{ -4 }$ & 6.5 \\
 ...    & ...   & 25 & &$ 7.8 \times 10^{ -5 }$ & 17 \\
 ...      & ...   & 50 & &$ 7.9 \times 10^{ -5 }$ & 12 \\
   ...    & ...   & 200 & &$ 1.2 \times 10^{ -4 }$ & $\mathbf{4.7}$ \\
   ...    & ...   & 400 & &$ 3.6 \times 10^{ -4 }$ & $\mathbf{1.2}$ \\
   ...     & 600  & 100 && $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ \\
   ...     & 1200  & 100 && $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ \\
  $    10^{ 8 }$ & 300 & 100 & & $ 6.6 \times 10^{ -4 }$ & $\mathbf{1.4}$ \\
...     & ...  & 25 & &$ 1.9 \times 10^{ -4 }$ & 12 \\
   ...     & ...  & 50 & &$ 3.3 \times 10^{ -4 }$ &
  $\mathbf{4.6}$ \\
     ...$^{\dagger}$ & ...  & 50& & $ 9.1 \times 10^{ -4 }$ &
  $\mathbf{5.6}$ \\
   ... & ... & 200 && $ 1.4 \times 10^{ -3 }$ &
  $\mathbf{0.43}$ \\
   ...     & 600  & 100 && $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ \\
   ...     & 1200  & 100 && $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ \\
  \hline
 & & & $\Gamma = 0.1$ & & & & & & \\
$    10^{ 6 }$ & 600  &25 & & $ 1.6 \times 10^{ -6 }$ & $ 1.6 \times 10^{ 3 }$ \\
  ...  & 600  & 50 & &$ 1.7 \times 10^{ -5 }$ & $\mathbf{33}$ \\
  ...  & 1200  & 100 && $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ \\
  $    10^{ 7 }$ & 1200  & 100& & $ 5.1 \times 10^{ -7 }$ & $ 9.4 \times 10^{ 4 }$ \\
  ...  & 600  & 50 && $ 4.5 \times 10^{ -5 }$ & $\mathbf{21}$ \\
  ...  & ...  & 25 & &$ 8.5 \times 10^{ -6 }$ & $ 4.6 \times 10^{ 2 }$ \\
$10^{8}$  & 300  & 50 & & $ 6.0 \times 10^{ -5 }$ & 56 \\
  ...  & 600  & 100 & &$ 8.0 \times 10^{ -4 }$ & $\mathbf{1.6}$ \\
  ...  &  ...  & 25 && $ 2.3 \times 10^{ -5 }$ & $ 2.8 \times 10^{ 2 }$ \\
  ...  &  ...  & 50 && $ 6.0 \times 10^{ -5 }$ & 56 \\
... & 1200 & 100 && $ 2.4 \times 10^{ -6 }$ & $ 2.1 \times 10^{ 4 }$ \\
  ...  & ...  & 50 && $ 2.0 \times 10^{ -6 }$ & $ 3.1 \times 10^{ 4 }$ \\
  ...  &  ...  & 200 && $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ \\
  ...  &  ... & 400 && $ 1.2 \times 10^{ -3 }$ & $\mathbf{4.6}$ \\
  \hline
\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
Eddington units, normalized to a stellar mass input parameter $\eta =
0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
stagnation radius.  Thermally unstable solutions are shown in bold
text.  $\dagger$Calculated with full radiative cooling included, assuming mass loss parameter $\eta = $? 
\end{tablenotes}
\end{minipage}
\end{threeparttable}
